\section{Purpose}
\subsection{General Purpose}

The main scope of this document is to define requirements for the application development, in order to make a correct project planification. 
To do this, we will analyze:

\begin{itemize}
\item System;
\item Functional and unfunctional requirements;
\item Constraints;
\item Relationships between stakeholders;
\item Possible scenarios and tests;
\end{itemize}
\medskip
These will be shown using different types of languages, starting from the natural language to the structured languages such as Alloy and UML.
Below, we will define the context in which our application will be developed.
During Sars-Cov-2 emergency, several countries imposed the lockdown in order to hinter the virus diffusion.
People had to change their habits, in fact they could go out only for necessary needs, such as going to the supermarket or pharmacy.
A lot of rules were introduced: not only using the masks or clean your hands but also keeping a social distance.
For instance people must pay attention while they're entering in the market due to the long queue, which could increase the possibility of virus diffusion.
This fact obliged people to stay for a long time standing up and waiting their turn losing a lots of time. 




\subsection{Goals}
\begin{description}
    \item[G1]User enters once arrived at the market
    \item[G2]Put a limit to the number of Users in the market
    \item[G3]Smart User can make a Reservation
    \item[G4]Smart User can make a Visit
    \item[G5]Mobile User can make a Reservation
    \item[G6]Mobile User can make a Visit
    \item[G7]Smart User can cancel a Booking
    \item[G8]Mobile User can cancel a Booking
\end{description}

 
\section{Scope}

The aim of the project is to develop an application which, thanks to an intuitive interface, will avoid a long waiting outside the market.
The application will provide a QR code as a virtual ticket on your own smartphone and to wait easily at home or everywhere instead of doing the physical queue for minutes or hours. 
In addition it will provide the position in queue and the time estimation of your turn.
The system will generate a QR code for the authentication at the entry, in order to verify the position in the queue. 
Moreover, the application gives the possibility to "book a visit" for who indicates the approximate expected duration of the visit and how many products they'll buy. \par \medskip
Although the reservation is made entirely with your smartphone, the market gives anyway the possibilities to provide the ticket locally on site, acting as proxies for the customers. This is mostly for aged people who are technologically backward or has no smartphone.
Once this procedure is completed, a SMS will be sent to the customers for noticing their turn. [todo]\par \medskip
In order to achieve the goal, we define the World, Machine and Shared Phenomena, which are really crucial to describe the system. They're characterized by fact that the first and the second ones are not visible among them; so we need a link between them which i represented by the Shared phenomena.






\subsection{World}
It's the portion of system to be developed. The main \textit{World Phenomena} are:

\begin{itemize}
\item Punctuality;
\item Loss of connection;
\item Respecting social distance;
\item Shopping duration;
\item Checking temperature;
\item Respecting social distance;
\end{itemize}

\subsection{Machine}
It represents the portion of system to be developed. The main \textit{Machine Phenomena} are:
\begin{itemize}
\item Average of shopping time;
\end{itemize}
\subsection{Shared Phenomena} 
They're phenomena shared between the World and the Machine which are controlled or observed by the system. In this scenario mainly are:

\begin{itemize}
\item Book/delete a visit in the supermarket;
\item Get a virtual ticket;
\item Send a notice;
\item Send a SMS;

\end{itemize}


\section{Definitions, Acronyms, Abbreviations}
\subsection{Definitions}

\begin{itemize}

\item \textbf{Mobilephone}: Elettronic device without CLup App;
\item \textbf{Smartphone}: Elettronic devide with Clup App; 
\item \textbf{CLup App}: It's the application described in this document. It's an application used to make and manage Booking in order to go grocery shopping;
\item \textbf{User}: Generic customer who plan to shop in the market. He could be a Smart or Mobile User;
\item \textbf{Smart User}: User who has got CLup App and so he's able to manage Booking by himself;
\item \textbf{Mobile User}: User who hasn't got CLup App and so he's not able to manage Booking by himself. For instance could be an User who has a dated mobile phone or simply he doesn't install the CLup App. A Mobile User allows a Receptionist to manage his booking by calling a telephone number by interacting with him;
\item \textbf{Shopping Size}: It's the dimensione of the grocery shopping. It could be \textit{Small}, \textit{Medium}, \textit{Large} depending on the number of items that is going to be purchased;  % [S 10, M 20, L 30];
\item \textbf{Booking}: It indicates the generic appointment of a User in the market. It could be a Reservation or a Visit;
\item \textbf{Reservation}: It's a type of Booking. Users simply book a seat at the market's queue. In addition User have to indicate the Shopping Size; 
\item \textbf{Visit}: It's a Booking planned in advance by Users. It is planned by putting the date and the range time in which the User is going grocery shopping. In addition User have to indicate the Shopping Size; 
\item \textbf{Reader}: It reads QRCode at the market's entrance. It allows User to go in;
\item \textbf{Booking submitted}: It means that the QRCode referred to the actual Booking is already submitted in the Reader;
\item \textbf{Visit activated}: It's a Visit which already booked but not yet submitted by the User;
\item \textbf{Reservation activated}: It's a Reservation which already booked but not yet submitted by the User;
\item \textbf{Waiting Time}: It's the time estimated by the system in which, by prevision, an User waits before he enters in the market;
\item \textbf{Shopping Time}: It's the time needed by a User to complete his own grocery shopping;
\item \textbf{Closure Time}: It's the range time in which the market is closed;
\end{itemize}

\begin{comment}


\item \textbf{Delayed ticket}: a ticket is delayed when, after the its ticket call, the user is not submit the QRCode in time (threshold of 1-2 minutes);
\item \textbf{Cancelled ticket}: a ticket is cancelled when it's already delayed and passed too much time (threshold of 15-20 minutes);
\item \textbf{BookingID}: string of n alphanumerical characters that is represented by the QRCode. If the user is not registered [...];


\end{comment}
\begin{itemize}
\subsection{Acronyms}
\item \textbf{RASD}: Requirement Analysis and Specification Document;
\item \textbf{HW}: Hardware;
\item \textbf{SW}: Hardware;
\item \textbf{API}: Application Programming Interface;
\end{itemize}


\subsection{Abbreviations}
\begin{itemize}
\item \textbf{App}: Application;
\end{itemize}

\section{Revision history}

\section{Reference Documents}

\section{Document Structure}

